master thesis

### 2018-03-25 Paper - Latex/Paper - Skizze - v4.tex
Paper - Discussion - Conclusion

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Metadata analysis}
    In order to generate a realistic simulation, influencing parameters are investigated. \\
    Since the transitions are minimized in an ancestral state reconstruction, this is an important 
      parameter to consider. On the other hand, the completeness of our input data are influencing 
      values. Therefore, two major types are distinguished:
    \begin{enumerate}
      \item Biological parameters (A result of the evolutionary process.):
        \begin{itemize}
          \item transition probabilities
        \end{itemize}
      \item Distribution of the loss of information:
        \begin{itemize}
          \item Loss of topology ($\rightarrow$ mutlifurcations)
          \item Unknown information about states of some leaf nodes
        \end{itemize}
    \end{enumerate}
    The influence of these parameters are tested on our result using our simulation (section 
      \ref{sec:simulation}).

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Simulation}\label{sec:simulation}
    The simulation compares these different of ancestral state reconstruction algorithms with each 
      other. \\
    First different implementations of the Fitch maximum parsimony are compared and then the best of 
      them is compared with the implementation of the Sankoff algorithm of the \textit{Castor} package 
      \cite{Louca2017}. \\

@@

  For this reconstruction, we first analyzed our data. This is the tree of OTL \cite{Hinchliff2015}
    and the data for the leaf nodes (free-living or parasite states) from GloBI \cite{Poelen2014} 
    (section \ref{sec:results - missing information}). \\
  Next we compared different possible methods. We decided to take a closer look at maximum parsimony 
    algorithms because they are best suited to the problem at hand. The reason for this can be found 
    in section \ref{sec:ancestral state reconstruction}. We tested these on different simulations of 
    the data and compared their predictive power (section \ref{sec:results of simulation}). \\
  We used the Sankoff algorithm \cite{Sankoff1975} implemented by Louca et al. \cite{Louca2017}, 
    which performs best, for the actual reconstruction on the real data. \\

  We then evaluated the results in two ways. On the one hand, we have examined the results of some 
    subtrees for their credibility with the help of biological background knowledge (subsection 
    \ref{sec:biological view}). On the other hand, we performed a leave-100-out cross validation
    (Subsection \ref{sec:results - cross validation}) and predicted approximately 98.17~\% states 
    correct.

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Results of simulation / Influence of different parameters} \label{sec:results of simulation}

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Results of the real data analysis created with Sankoff}
    This section is about evaluating the prediction of real data using the Sankoff method. \\
    It is divided into two subsections. \ref{sec:biological view}: The analysis of some subtrees using 
      biological background knowledge. \ref{sec:results - cross validation}: Presentation of the results 
      of the leave-100-out cross validation.

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Biological view} \label{sec:biological view}
      To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
        selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
        Apicomplexa. \\
      In Table \ref{table:phylum leaf nodes states} we compare the given states with the predicted ones. \\
      Several factors such as the distribution of existing input data via parasitics and free-livings, 
        faulty input data from GloBI and reinforcement of errors by multifurcation play an important 
        role, which crystallize out in these examples. \\
      An important factor here is that the credibility of the results. The accuracy of the input data 
        stands and falls with the presence and the correctness of the data of GloBI. Errors of incorrect 
        input data can be amplified by incorrect prediction of unknown species and can be reversed in 
        order to improve the data situation of GloBI. \\
      Since we look at such large trees we can not expect to know all the parasites, so we look at 
        individual positives. This is positive in the sense that the majority have the opposite state.

@@

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Origins and Losses}

@@

  Die simulation ergab: x \\
  Der biological view ergab: y \\
  Die leave-100-out cross validation ergab: z

>>>>

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Metadata analysis}
    In order to generate a realistic simulation, influencing parameters are investigated. \\
    Since the transitions are minimized in an ancestral state reconstruction, this is an important 
      parameter to consider. On the other hand, the completeness of our input data are influencing 
      values. Therefore, two major types are distinguished:
    \begin{enumerate}
      \item Biological parameters (A result of the evolutionary process.):
        \begin{itemize}
          \item transition probabilities
        \end{itemize}
      \item Distribution of the loss of information:
        \begin{itemize}
          \item Loss of topology ($\rightarrow$ mutlifurcations)
          \item Unknown information about states of some leaf nodes
        \end{itemize}
    \end{enumerate}
    The influence of these parameters are tested on our result using our simulation (section 
      \ref{sec:methods - simulation}).

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Simulation}\label{sec:methods - simulation}
    The simulation compares these different of ancestral state reconstruction algorithms with each 
      other. \\
    First different implementations of the Fitch maximum parsimony are compared and then the best of 
      them is compared with the implementation of the Sankoff algorithm of the \textit{Castor} package 
      \cite{Louca2017}. \\

@@

  For this reconstruction, we first analyzed our data. This is the tree of OTL \cite{Hinchliff2015}
    and the data for the leaf nodes (free-living or parasite states) from GloBI \cite{Poelen2014} 
    (section \ref{sec:results - missing information}). \\
  Next we compared different possible methods. We decided to take a closer look at maximum parsimony 
    algorithms because they are best suited to the problem at hand. The reason for this can be found 
    in section \ref{sec:ancestral state reconstruction}. We tested these on different simulations of 
    the data and compared their predictive power (section \ref{sec:results - simulation}). \\
  We used the Sankoff algorithm \cite{Sankoff1975} implemented by Louca et al. \cite{Louca2017}, 
    which performs best, for the actual reconstruction on the real data. \\

  We then evaluated the results in two ways. On the one hand, we have examined the results of some 
    subtrees for their credibility with the help of biological background knowledge (subsection 
    \ref{sec:results - biological view}). On the other hand, we performed a leave-100-out cross validation
    (Subsection \ref{sec:results - cross validation}) and predicted approximately 98.17~\% states 
    correct.

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Results of simulation / Influence of different parameters} \label{sec:results - simulation}

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Results of the real data analysis created with Sankoff}
    This section is about evaluating the prediction of real data using the Sankoff method. \\
    It is divided into two subsections. \ref{sec:results - biological view}: The analysis of some subtrees using 
      biological background knowledge. \ref{sec:results - cross validation}: Presentation of the results 
      of the leave-100-out cross validation.

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Biological view} \label{sec:results - biological view}
      To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
        selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
        Apicomplexa. \\
      In Table \ref{table:phylum leaf nodes states} we compare the given states with the predicted ones. \\
      Several factors such as the distribution of existing input data via parasitics and free-livings, 
        faulty input data from GloBI and reinforcement of errors by multifurcation play an important 
        role, which crystallize out in these examples. \\
      An important factor here is that the credibility of the results. The accuracy of the input data 
        stands and falls with the presence and the correctness of the data of GloBI. Errors of incorrect 
        input data can be amplified by incorrect prediction of unknown species and can be reversed in 
        order to improve the data situation of GloBI. \\
      Since we look at such large trees we can not expect to know all the parasites, so we look at 
        individual positives. This is positive in the sense that the majority have the opposite state.

@@

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Origins and Losses} \label{sec:results - origins and losses}

@@

    From the simulation, we can conclude that we predict correctly about 60\% of the nodes in the 
      present data situation (see section \ref{sec:results - simulation}).
    The leave-100-out cross validation even showed that we predict the omitted nodes to be 98.17~\%  
      percent correct (see section \ref{sec:results - cross validation}). \\
    This allows for the assumption that the data is grouped and not uniformly distributed and thus 
      smaller subtrees are present in which data are to be found in the simulation with smaller 
      multifurcation and smaller value for unknown nodes. This is also confirmed by our biological 
      analysis of the Chordata subtree (see subsection \ref{sec:results - biological view}). \\
    However, this means that the ancestral states' data in the direction of root node are probably 
      particularly unbelievable. Which makes the localization of Origins direction root node 
      difficult. The question remains, how much this affects the estimation of the number of origins. 
      Our comparison with the paper from Weinstein and Kuris \cite{Weinstein2016} (see subsection 
      \ref{sec:results - origins and losses}), however, leaves us with optimism.
